---
title: "4_case_study"
author: "Wenxin Tian"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggridges)
```

```{r}
library(p8105.datasets)
data(nyc_airbnb)
```

## Brainstorm Questions:

- Where are Airbnbs most expensive?
- Which units have the most availability?
- How is review score impacted by locations?
- How many units are run by hosts who have multiple units? Does that impact pricing?

## Attempt Solutions:

__Where are Airbnbs most expensive?__
```{r}
nyc_airbnb |>
  count(neighbourhood_group)

nyc_airbnb |>
  group_by(neighbourhood_group, room_type) |>
  summarize(mean_price = mean(price)) |> 
  arrange(desc(mean_price)) |>
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
  
nyc_airbnb |>
  group_by(neighbourhood_group, room_type) |>
  summarize(median_price = median(price)) |> 
  arrange(desc(median_price)) |>
  pivot_wider(
    names_from = room_type,
    values_from = median_price
  )

nyc_airbnb |>
  filter(price < 1000, room_type == "Entire home/apt") |>
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(room_type ~ neighbourhood_group)
```

```{r}
nyc_airbnb |>
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    neighbourhood_group == "Manhattan") |>
  group_by(neighbourhood) |>
  summarize(mean_price = mean(price)) |>
  arrange(desc(mean_price)) |>
  ggplot(aes(x = neighbourhood, y = mean_price)) +
  geom_col()
```

```{r}
nyc_airbnb |>
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    neighbourhood_group == "Manhattan") |>
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |>
  ggplot(aes(x = price, y = neighbourhood)) +
  geom_density_ridges()
```

## Try to make a map with coordinates:

```{r}
nyc_airbnb |>
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    neighbourhood_group == "Manhattan") |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```

__Leaflet:__

```{r}
library(leaflet)

nyc_airbnb |>
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    neighbourhood_group == "Manhattan") |>
  sample_n(500) |>
  leaflet() |>
  addTiles() |>
  addCircleMarkers(~lat, ~long, radius = .5)
```

__How is review score impacted by locations?__

```{r}
nyc_airbnb |>
  group_by(neighbourhood_group) |>
  summarize(mean_review_score = mean(review_scores_location, na.rm = TRUE)) |>
  arrange(desc(mean_review_score))
```

__How many units are run by hosts who have multiple units? Does that impact pricing?__

```{r}
multiple_unit_hosts =
  nyc_airbnb |>
  group_by(host_id) |>
  summarize(number_of_units = n()) |>
  filter(number_of_units > 1) |>
  arrange(desc(number_of_units))

# Multiple unit mean price:

nyc_airbnb |>
  filter(host_id %in% pull(multiple_unit_hosts, host_id)) |>
  summarize(mean_price = mean(price))

# Overall mean price:

nyc_airbnb |>
  summarize(mean_price = mean(price))
```


